---
title: "Naming Conventions for Code Used in Learning"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Naming Conventions for Code Used in Learning}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(useclinic)
```

# The Upside

The `useclinic` package creates other packages for distribution to learners. The
created-package structure, assuming two topics "intro" and "advanced", looks like:

```
DESCRIPTION
NAMESPACE
data/
data-raw/
man/
R/
  aaa_internal.R
  advanced_data.R
  advanced_functions.R
  advanced_plotting.R
  checks.R
  intro_data.R
  intro_functions.R
  intro_plotting.R
  plotting.R
  utilities.R
inst/
  scripts/                   # ... if the topics have practicals
    advanced/Step_00.R
    intro/Step_00.R
    solutions/
      advanced/Step_00.R
      intro/Step_00.R
  tutorials/                 # ... if the topics have tutorials
    advanced/advanced.Rmd
    intro/intro.Rmd
```

The created files have guidance comments, example code in the preferred style,
and assorted preconstructed scaffolding.

# Motivation

The `useclinic` package reflects one of [ICI3D](https://www.ici3d.org) goals: to
incubate training activities, in service of improving public health. Our main
focus is modelling and analysis, which are very programming-oriented activities,
and much of the field uses `R`. So: we have developed a package factory, which
incorporates the lessons we've learned about providing good materials.

The `useclinic` package extends the `usethis` package to apply our conventions
automatically when generating new learning materials. We organize our workshops
and clinics typically by "topics" - think of these as chapters in a book. They
tend to be a coherent element of the overall coursework, and identifiable with
a succinct label, though they also build upon (and in turn are built upon by)
other material. We try to maintain a consistent "feel" across topics - e.g.
similar visualizations and coding conventions across activities. We prefer to
avoid minor distractions like changing color schemes, fonts, labels, and so on -
this lets participants focus on key learning tasks.

We also prefer to remove as much friction from our activities as possible. We
typically cover a lot of material, so we try to avoid anything that slows people
down and incorporate approaches that speed up working with the material.

# Organizing Conventions

Given that motivation, `useclinic` creates package skeletons that follow these
conventions:

## Practicals, Tutorials, Data, and Code

The purpose of learning packages is provide materials for learning activities.
As such, we include templates for "practicals" i.e. plaintext `R` scripts
intended to be editted by learners, and we include templates for `learnr`-based
interactive `rshiny` applications.

We also use templates for data and code. Many computational exercises concern
the ingestion, cleaning, and analysis of data, so including data in these
packages is a frequent need.

Lastly, this is a R programming language package - there should be `R` code! In
keeping with our motivations, we're typically providing code to replace what
learners would otherwise have to 1) write, but isn't really the point of the
work, or 2) scroll past extensively. However, these are still functions that
they still might to select among or be curious to see the internals of, so we
encourage particular naming conventions (see the [last section](#naming)),
thorough documentation *as well as* internal commenting in the function body -
because those comments are visible when inspecting the function!

One final note about code: we also tend to provide functions that 1) apply
across several topics and 2) the mimic or enhance the functionality provided in
other packages (e.g. `ggplot2` themes, scales, geoms, ...). For those cases,
we do not use the "topic" style naming, but instead generally promote "pothole"
case (as consistent with how we approach prepending topics to functions) and/or
adopting the style of the mimicing or extended package.

## Topics

To gather together related practicals, tutorials, data, and code, we use
"topics": shorthand, descriptive names for a general collection of bits that go
together. The choice what features to categorize on is up to you; we often find
the typical lecture+practical divisions are good. Imagine you had a few
discussions plus practicals on probability, followed by a couple on statistics.
You might then choose to organize by topics "prob" and "stat".

These topics then inform the location and/or naming of files, functions, and
data (though their internal titles can be more detailed).

## Naming

Finally, we apply topics as follows:

 - for functions primarily used in the context of a particular topics activties,
 they should be named in the style `topic_descriptive_name`. Then, when learners
 are writing with the package, they can type `yourpkgname::topic_`+tab a see
 proposals for all the relevant functions.
 - these functions should generally be gathered together into a small number of
 source files. We typically use `topic_functions.R`, `topic_plotting.R` and
 (if data are present) `topic_data.R` (for documentation) and in the package
 `data-raw/` directory, source for generating those data as `topic_DATANAME.R`.
 The `topic_function.R` file covers general functions for the topic, while
 `topic_plotting.R` should focus on visualization and data rearrangement
 pertinent to visualization. You may find other small groups sensible as well -
 e.g. `topic_storage.R` might be relevant if you have learners do lots of
 reading / writing of data in non-visual formats. Feel free to use them!
 We provide some functionality to take advantage of the "topic" naming
 convention, but that only concerns itself with prefixes.
 - for non-code, non-in-session-data materials, i.e. those distributed via the
 `inst` directory, we create (as requested) `practicals` and `tutorials`
 subdirectories. As relevant, these subdirectories have source scripts (and
 solutions) and the source Rmarkdown / `learnr` application files for the
 tutorials. Note: using the tutorials file will cause `Rstudio` to display the
 tutorial under its table of contents for available tutorials.
