---
title: "{{{fullname}}}"
output: learnr::tutorial
runtime: shiny_prerendered
description: >
  In the Rstudio -> Tutorial tab, this tutorial will be finable as
  {{{fullname}}} (in bold), with a subscript {{{pkgname}}}: {{{sessname}}},
  followed by this text as a description.
---

```{r setup, include=FALSE}
library(learnr)
library({{{pkgname}}})
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This template is provided by `useclinic` for package `{{{pkgname}}}`. For 
`learnr` details, [see their documents](https://rstudio.github.io/learnr/reference/index.html).
The exercise chunk options can be found [here](https://rstudio.github.io/learnr/reference/tutorial_options.html).

## Example Topic

Some discussion, motivation, etc.

### Demo Exercise 

*This is the basic exercise code chunk.*

Write the R code required to print "Hello World!":

```{r hw, exercise=TRUE}

```

### Demo Exercise II

*Exercise chunks can be prepopulated, and pre-allocated more working lines via e.g. `exercise.lines = 5`.*

Complete the `helloworld` function to take an argument and greet it.

```{r hw-two, exercise=TRUE, exercise.lines = 5}
helloworld <- function(name) {
  
}
```

### Exercise with Evaluation

*Exercise chunks can be pre-evaluated via the `exercise.eval` option, for use in before- vs after- activities.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

*Reusing chunk labels with "-hint" appended has special behavior.*

```{r print-limit-hint}
mtcars |> head()
```

## Example Quizzes

In addition to exercise blocks, tutorials also support quizzes. Use `quiz()` to
group one or more questions. Questions can be made via `question()` (with type
inferred) or with one of several `question_...()` functions from `learnr`.

### Basics

```{r quiz1}
quiz(
  # single select:
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  # multi-select:
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

## Free Response "Quiz"

Unless actively deleted (it is included in the default utilities script from `useclinic`), you can also use the `question_freeresponse` to pose more complex questions and then reply with an example answer for users to consider, rather than attempting to mark the result correct or incorrect.

```{r freeresponse_eg}
quiz(
  question_freeresponse(
    "Describe some complex phenomena.",
    "Lorem ipsum."
  )
)
```

